Nested sampling with two objective functions

### 2016-02-09 Paper/ms.tex
Updated abstract

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{We present a generalization of the Nested Sampling algorithm for
estimating the partition function $Z(\beta_1, \beta_2)$ of a family of
probability distributions indexed by two hyperparameters $\beta_1$ and
$\beta_2$. These
problems arise frequently in statistical mechanics and occasionally in
Bayesian inference. We demonstrate the algorithm on a toy example where
$Z(\beta_1, \beta_2)$ is known, and show empirically that the accuracy
improves as XX as a function of the number of particles $N$. We also
calculate the partition function for a Lennard-Jones system in an external
field, as a function of the external field strength, in a single run.}

>>>>

% Abstract (Do not use inserted blank lines, i.e. \\)
\abstract{We present a generalization of the Nested Sampling algorithm for
estimating the partition function $Z(\beta_1, \beta_2)$ of a family of
probability distributions indexed by two hyperparameters $\beta_1$ and
$\beta_2$. These
problems arise frequently in statistical mechanics and occasionally in
Bayesian inference. We demonstrate the algorithm on three example problems.
The first is a simple toy example where
$Z(\beta_1, \beta_2)$ is known, where we show empirically how the accuracy
improves as a function of the number of particles $N$. We also
calculate the partition function for a collection of atoms with a potential
that is `intermediate' between a Lennard-Jones form and a polymer form, in
a single run. Finally, we present a Bayesian image reconstruction example,
where we can infer the value of a hyperparameter even though its prior
distribution contains an `intractable' normalizing constant.}
